### 2024-12-25 mixed-models.qmd
20241225 - plot tweaks

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_randomLinearFixedQuadraticSlopes,
    color = positionFactor
  )
) + 
  geom_line(linewidth = 2) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Mixed Model with Random Intercepts, Random Linear Slopes, and Fixed Quadratic Slopes"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_randomLinearFixedQuadraticSlopesInteraction,
    color = positionFactor
  )
) + 
  geom_line(linewidth = 2) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Mixed Model with Random Intercepts, Random Linear Slopes, and Fixed Quadratic Slopes\nin Interaction With Position"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_quadratic,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Quadratic Model with All Players",
    color = "Position"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_depthQuadratic,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Quadratic Model with Players Who Were Once at Top of End-of-Season Depth Chart",
    color = "Position"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_gam,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Generalized Additive Model with All Players",
    color = "Position"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_depthGAM,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Generalized Additive Model with Players Who Were Once at Top of End-of-Season Depth Chart",
    color = "Position"
  ) +
  theme_classic()
```

>>>>

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_randomLinearFixedQuadraticSlopes,
    color = positionFactor
  )
) + 
  geom_line(linewidth = 2) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Mixed Model with Random Intercepts, Random Linear Slopes, and Fixed Quadratic Slopes",
    color = "Position"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_randomLinearFixedQuadraticSlopesInteraction,
    color = positionFactor
  )
) + 
  geom_line(linewidth = 2) +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Mixed Model with Random Intercepts, Random Linear Slopes, and Fixed Quadratic Slopes\nin Interaction With Position",
    color = "Position"
  ) +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_quadratic,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Quadratic Model with All Players",
    color = "Position"
  ) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(fill = NA))) # transparent legend background
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_depthQuadratic,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Quadratic Model with Players Who Were Once at Top of End-of-Season Depth Chart",
    color = "Position"
  ) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(fill = NA))) # transparent legend background
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_gam,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Generalized Additive Model with All Players",
    color = "Position"
  ) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(fill = NA))) # transparent legend background
```

@@

ggplot2::ggplot(
  data = pointsPerSeason_positionAge_newData,
  mapping = aes(
    x = age,
    y = fantasyPoints_depthGAM,
    color = positionFactor
  )
) + 
  geom_smooth() +
  labs(
    x = "Player Age (years)",
    y = "Fantasy Points (Season)",
    title = "Fantasy Points (Season) by Player Age and Position",
    subtitle = "Generalized Additive Model with Players Who Were Once at Top of End-of-Season Depth Chart",
    color = "Position"
  ) +
  theme_classic() +
  guides(color = guide_legend(override.aes = list(fill = NA))) # transparent legend background
```
